---
title: "MassDEP_NBCtools"
author: "Ben.Block@tetratech.com"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{MassDEP_NBCtools}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# Introduction

`MassDEP_NBCtools` was created by Tetra Tech, Inc. in 2022 to meet the needs of Massachusetts Department Environmental Protection Agency (MassDEP) staff to evaluate water quality at sites and assessment units for natural background conditions. The core purpose of this package is to run a web-based Shiny application that has the user walk through a series of questions and review steps to determine whether a water quality exceedance could be due solely to natural conditions (as opposed to anthropogenic causes).

It is envisioned that this library will be a living program and will add additional functions and routines in the future.

# Installation

The R library is saved on GitHub (<https://github.com/Blocktt/MassDEP_NBCtools>) for ease of updating and distribution. Issues can be tracked, fixed, and code is available for download. Current users of `MassDEP_NBCtools` can update the library using the same code used to install the library (see below). Devtools is required to download from GitHub.

At this time, there are no plans to submit `MassDEP_NBCtools` to CRAN (R's library repository).

### `MassDEP_NBCtools`, Download Instructions

```{r install_MassDEP_NBCtools, eval=FALSE}
install.packages("devtools")
library(devtools)
install_github("Blocktt/MassDEP_NBCtools", force=TRUE, build_vignettes=TRUE)
```

To contact the author directly email [Ben.Block\@tetratech.com](mailto:Ben.Block@tetratech.com){.email}.

# Packages

Several packages were used to build the functionality in `MassDEP_NBCtools`:

`dplyr` `shiny` `shinydashboard` `ggplot2` `leaflet`

To install packages follow the example of the code below for installing `dplyr`.

```{r install_other, eval=FALSE}
install.package("dplyr")
```
